Share Buyback and Equity Issue Anomalies Revisited

### 2016-03-19 bb_issuers.Rnw
update paper

\noindent \textit{JEL classification}: G35

\medskip
\noindent \textit{Keywords}: Share Buybacks, Seasoned Equity Offerings

@@

One straightforward explanation is that they are not really anomalous returns but compensation for risk. Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the Carhart (1997) 4-factor model as benchmarks. However, \cite{FamaFrench2015b}  argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns (Novy-Marx (2013)). If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization (Stephens and Weisbach (1998)). Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the "buyback sample". But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in "net issues" assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from "old" selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only takes advantage of selling shareholders who leave the firm. In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.

Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the Fama and French (2015b) conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. The interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries. The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.

@@

The results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously. Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information. If the buyback signals a change in risk (\cite{GrullonMichaely2004}) hedging market risk may be complicated. That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios. We show that an investor who followed this strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.

The second major purpose of this paper is to test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}, i.e. (idiosyncratic) volatility is negatively related to expected returns. For example, \cite{Ang2006} find negative alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model. Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms. However, in our buyback sample we find a significant positive relation between excess returns, using the Fama-French 5-factor model as a benchmark. This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market. The result is also consistent with the  {\it costly arbitrage hypothesis} of \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued  stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  Their argument is that idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.  So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.

Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns. This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks (\cite{IkenberryVermaelen1996}). If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.

Combining idiosyncratic risk and total volatility with the Peyer and Vermaelen (2009) Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

@@

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of share authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

For the issuers, we started with \Sexpr{cleanup_iss$Standardise$SDC_initial_data} events from SDC, filtered to exclude rights issues, pure secondary offerings where existing shareholders sell shares without generating proceeds for the company,  issues made by non-U.S. firms or in non-U.S. markets, issues made by closed-end funds or unit investment trusts, as well as block trades, accelerated offers and best efforts. We removed all SDC events for which either the event date (\Sexpr{cleanup_iss$Standardise$SDC_NODATE} events) or the CUSIP (\Sexpr{cleanup_iss$Standardise$SDC_NOCUSIP} events) was missing or where we found duplicate events with mismatching information (\Sexpr{cleanup_iss$Standardise$BAD_DUPLICATES} events), a total of \Sexpr{cleanup_iss$Standardise$SDC_standardize_removal} events - given the overlap between these cases. Finally, as for the buybacks, we removed the following events: no CRSP returns available (\Sexpr{cleanup_iss$get_crsp$NOPERMNO_remove + cleanup_iss$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_iss$compustat$NO_GVKEY_remove + cleanup_iss$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events). We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(ISSUERS_DATA$finance_Size_used)} events). Our final sample contains \Sexpr{length(cusip_iss)} issuers events made by \Sexpr{length(unique(cusip_iss))} firms. The average percent of shares issued was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).

@@

Table~\ref{tbl:priorBuybacks}, Panel~A, shows long-term cumulative excess returns for various holding periods after the announcement using the Ibbotson RATS event study method. Each event month~$t$ we run cross-sectional regressions of stock returns against the factors. The intercept in the regression measures the average abnormal excess return in event month~$t$. We then accumulate these excess returns over various time horizons (up to 48 months after the event). The advantage of this method is that each event gets the same weight and that factor betas are allowed to change in event time, something that may be important as capital structure changes may signal a change in risk~\citep{GrullonMichaely2004}. The table compares the excess returns using the \cite{FamaFrench1993} three-factor model and the \cite{FamaFrench2015a} five-factor model. The results show that, although using a five-factor model lowers excess returns, the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{IRATS_table_all_bb["+48","CAR 5F"]}$\%$ after 4 years (t=\Sexpr{IRATS_table_all_bb["+48",5]}). So the buyback anomaly does not disappear when we use a five-factor model. In all the tables we also calculate cumulative excess returns in the 6 months prior to the buyback. Consistent with past research (e.g., \cite{PeyerVermaelen2009}) buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(IRATS_table_all_bb[reported_times[1],1],0)}$\%$. This is consistent with the hypothesis that the typical repurchase announcement is triggered by at least the perception of insiders that the stock is undervalued.

Table~\ref{tbl:priorIssuers}, Panel~A, shows the results for all equity issues, using the same methodology as in Table~\ref{tbl:priorBuybacks}, Panel~A. Our results are largely consistent with \cite{FamaFrench2015b}. Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of \Sexpr{IRATS_table_all_iss["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_all_iss["+48",2]}). However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months. This shows that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure. Unlike buybacks, equity issues are firm commitments and announced and completed at the same point in time. Using actual shares issued (the measure used by Fama-French (1995b)) and equity announcements (our measure) should therefore produce similar results. Buyback authorization announcements on the other hand are not firm commitments and are often executed over a long period after the announcement. Actual repurchase dates thus do not correspond to announcement dates. Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss[reported_times[1],1],0)}$\%$ in the 6 months prior to the equity issue. However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that these firms experienced a substantial increase in growth opportunities and issued equity to finance them. 
One critique of the \cite{ibbotson1975} RATS method is that the result may be time-specific. Indeed as every event is equally weighted the cumulative average abnormal returns are dominated by periods when there are a large number of events. So we also use the Calendar Time method where in each calendar month we form an equally-weighted portfolio of all firms that announce a buyback (or an equity issue) in the previous $t$~months. We then run a time series regression of the portfolio returns against the factors. The intercept of the regression is the average monthly excess return in the $t$~months after the event.

The results in Panel~B of Tables \ref{tbl:priorBuybacks} and  \ref{tbl:priorIssuers} are similar to Panel~A of the same tables. Abnormal returns after buybacks are smaller when the five-factor model is used but remain statistically significant over all horizons. For example, over the 48 month horizon the average monthly excess return is \Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$ (t=\Sexpr{CAL_table_all_bb["+48",5]}) which corresponds to \Sexpr{48*CAL_table_all_bb["+48","CAL 5F"]}$\%$ over 48 months. Note also that excess returns fall when the investment horizon increases. The largest monthly excess return (\Sexpr{CAL_table_all_bb["+1","CAL 5F"]}$\%$) is earned by the portfolio that holds buyback stocks for one month  (not reported in Table \ref{tbl:priorBuybacks})  and the smallest excess return (\Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$) is earned by the portfolio that picks buybacks announced during the previous 48 months. This clearly shows that forming portfolios after buybacks are completed (as is done by measuring net issues in \cite{FamaFrench2015b}) is introducing a downward bias as many repurchase programs are completed several months (sometimes years) after the buyback announcement. Waiting until the buyback is completed means missing the largest excess returns earned shortly after the buyback authorization. Finally, there are no statistically significant excess returns after equity issues, regardless whether we use the three or five-factor model.

@@

Of the \Sexpr{length(SEO_exit_days)} such events, \Sexpr{sum(abs(SEO_exit_days) < 1*365)} happen within 1 year from the buyback announcement, \Sexpr{sum(abs(SEO_exit_days) < 2*365)} happen within 2 years and \Sexpr{sum(abs(SEO_exit_days) < 3*365)} happen within 3 years. Note that this grouping of the events is done with hindsight: it is not possible to know at the time of the buyback announcement whether there will be a subsequent SEO or not. We are simply asking the question whether those firms that announced a buyback when they appeared undervalued issued equity when they were overvalued. Figure~\ref{fig:BBISSevents} shows the percentage of repurchasing firms that announced an equity issue within 48 months. The average percentage is \Sexpr{round(mean(BB_with_ISS_later_total),1)}$\%$ and there are only \Sexpr{sum(BB_with_ISS_later_total > 10)} years (1989 and 1990) where the percentage is larger than $10\%$.

@@

The Calendar Method results in Panel B of Table~\ref{tbl:BBISSexit} show a relatively large drop of the excess returns over time (e.g., from \Sexpr{Exit_on_SEO_Abn_table_cal["+12",4]}$\%$ after 12 months to \Sexpr{Exit_on_SEO_Abn_table_cal["+48",4]}$\%$ after 48 months) indicating potential benefits of exiting a buyback position when there is a subsequent issue. Figure  \ref{fig:BBISSexit} (Panel~B) shows the benefits of exiting early. The figure shows a strategy with hindsight where, starting in \Sexpr{firstyear}, we invest in an equally weighted portfolio of only firms that announced a buyback and subsequently issued equity within the 48 months after the buyback announcement. The dashed line shows the cumulative excess return if we sold the stock whenever the firm issued shares within 48 months (the exit strategy). The solid line shows the cumulative excess returns if we sold 48 months after the buyback announcement (the no exit case). The investor who had followed the exit strategy would have earned (after 30 years) a cumulative excess return of \Sexpr{round(tail(100*cumsum(BB_ISS_Exit_Hedged),1),1)}$\%$, significantly larger than the \Sexpr{round(tail(100*cumsum(BB_ISS_NoExit_Hedged),1),1)}$\%$ of a buy hold for 48 months strategy. Note, however, that because very few firms that buy back stock issue equity within 48 months,  a strategy ``without hindsight'' where one bought all companies after a buyback and sold only those after a subsequent equity issue would not substantially increase excess returns.

>>>>

\noindent  \textit{JEL classification}: G35; G14; G32

\medskip
\noindent \textit{Keywords}: Share Buybacks; Seasoned Equity Offerings; Anomalies

@@

One straightforward explanation is that they are not really anomalous returns but compensation for risk. Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks. However, \cite{FamaFrench2015b}  argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}. If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization \citep{StephensWeisbach1998}. Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the ``buyback sample''. But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm. In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.

Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. An interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries. The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.

@@

The results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously. Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information. If the buyback signals a change in risk \citep{GrullonMichaely2004} hedging market risk may be complicated. That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios. We show that an investor who followed such a strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.

The second major purpose of this paper is to test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}, i.e. (idiosyncratic) volatility is negatively related to expected returns. For example, \cite{Ang2006} find {\it negative} alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model. Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms. However, in our buyback sample we find a significant {\it positive} relation between excess returns, using the Fama-French 5-factor model as a benchmark. This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market. The result is also consistent with the  {\it costly arbitrage hypothesis} of \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued  stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  Their argument is that idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.  So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.

Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns. This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks \citep{IkenberryVermaelen1996}. If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.

Combining idiosyncratic risk and total volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

@@

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

For the issuers, we started with \Sexpr{cleanup_iss$Standardise$SDC_initial_data} events from SDC, filtered to exclude rights issues, pure secondary offerings where existing shareholders sell shares without generating proceeds for the company,  issues made by non-U.S. firms or in non-U.S. markets, issues made by closed-end funds or unit investment trusts, as well as block trades, accelerated offers and best efforts. We removed all SDC events for which either the event date (\Sexpr{cleanup_iss$Standardise$SDC_NODATE} events) or the CUSIP (\Sexpr{cleanup_iss$Standardise$SDC_NOCUSIP} events) was missing or where we found duplicate events with mismatching information (\Sexpr{cleanup_iss$Standardise$BAD_DUPLICATES} events), a total of \Sexpr{cleanup_iss$Standardise$SDC_standardize_removal} events - given the overlap between these cases. Finally, as for the buybacks, we removed the following events: no CRSP returns available (\Sexpr{cleanup_iss$get_crsp$NOPERMNO_remove + cleanup_iss$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_iss$compustat$NO_GVKEY_remove + cleanup_iss$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events). We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(ISSUERS_DATA$finance_Size_used)} events). Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms. The average percent of shares issued was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).

@@

Table~\ref{tbl:priorBuybacks}, Panel~A, shows long-term cumulative excess returns for various holding periods after the announcement using the Ibbotson RATS event study method. Each event month~$t$ we run cross-sectional regressions of stock returns against the factors. The intercept in the regression measures the average abnormal excess return in event month~$t$. We then accumulate these excess returns over various time horizons (up to 48 months after the event). The advantage of this method is that each event gets the same weight and that factor betas are allowed to change in event time, something that may be important as capital structure changes may signal a change in risk~\citep{GrullonMichaely2004}. The table compares the excess returns using the \cite{FamaFrench1993} three-factor model and the \cite{FamaFrench2015a} five-factor model. The results show that, although using a five-factor model lowers excess returns, the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{IRATS_table_all_bb["+48","CAR 5F"]}$\%$ after 4 years (t=\Sexpr{IRATS_table_all_bb["+48",5]}). So the buyback anomaly does not disappear when we use a five-factor model. In all the tables we also calculate cumulative excess returns in the 6 months prior to the buyback. Consistent with past research [see e.g., \citep{PeyerVermaelen2009}] buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(IRATS_table_all_bb[reported_times[1],1],0)}$\%$. This is consistent with the hypothesis that the typical repurchase announcement is triggered by a stock price decline that insiders may feel is not justified given their long-term prospects about the company.

Table~\ref{tbl:priorIssuers}, Panel~A, shows the results for all equity issues, using the same methodology as in Table~\ref{tbl:priorBuybacks}, Panel~A. Our results are largely consistent with \cite{FamaFrench2015b}. Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of \Sexpr{IRATS_table_all_iss["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_all_iss["+48",2]}). However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months. This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure. Unlike buybacks, equity issues are firm commitments and announced and completed at the same point in time. Using actual shares issued, the measure used by \cite{FamaFrench2015b}, and equity announcements (our measure) should therefore produce similar results. Buyback authorization announcements on the other hand are not firm commitments and are often executed over a long period after the announcement. Actual repurchase dates thus do not correspond to announcement dates. Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss[reported_times[1],1],0)}$\%$ in the 6 months prior to the equity issue. However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.

One critique of the \cite{ibbotson1975} RATS method is that the result may be time-specific. Indeed as every event is equally weighted the cumulative average abnormal returns are dominated by periods when there are a large number of events. So we also use the Calendar Time method where in each calendar month we form an equally-weighted portfolio of all firms that announced a buyback (or an equity issue) in the previous $t$~months. We then run a time series regression of the portfolio returns against the factors. The intercept of the regression is the average monthly excess return in the $t$~months after the event. The results are shown in Panel~B of Tables \ref{tbl:priorBuybacks} and  \ref{tbl:priorIssuers} and are similar to Panel~A of the same tables. Abnormal returns after buybacks are smaller when the five-factor model is used but remain statistically significant over all horizons. For example, over the 48 month horizon the average monthly excess return is \Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$ (t=\Sexpr{CAL_table_all_bb["+48",5]}) which corresponds to \Sexpr{48*CAL_table_all_bb["+48","CAL 5F"]}$\%$ over 48 months. Note also that excess returns fall when the investment horizon increases. The largest monthly excess return (\Sexpr{CAL_table_all_bb["+1","CAL 5F"]}$\%$) is earned by the portfolio that holds buyback stocks for one month  (not reported in Table \ref{tbl:priorBuybacks})  and the smallest excess return (\Sexpr{CAL_table_all_bb["+48","CAL 5F"]}$\%$) is earned by the portfolio that picks buybacks announced during the previous 48 months. This clearly shows that forming portfolios after buybacks are completed, as is done by measuring net issues in \cite{FamaFrench2015b}, is introducing a downward bias as many repurchase programs are completed several months (sometimes years) after the buyback announcement. Waiting until the buyback is completed means missing the largest excess returns earned shortly after the buyback authorization. Finally, there are no statistically significant excess returns after equity issues, regardless whether we use the three or five-factor model.

@@

Of the \Sexpr{length(SEO_exit_days)} such events, \Sexpr{sum(abs(SEO_exit_days) < 1*365)} SEOs happen within 1 year from the buyback announcement, \Sexpr{sum(abs(SEO_exit_days) < 2*365)} happen within 2 years and \Sexpr{sum(abs(SEO_exit_days) < 3*365)} happen within 3 years. Note that this grouping of the events is done with hindsight: it is not possible to know at the time of the buyback announcement whether there will be a subsequent SEO or not. We are simply asking the question whether those firms that announced a buyback when they appeared undervalued issued equity when they were overvalued. Figure~\ref{fig:BBISSevents} shows the percentage of repurchasing firms that announced an equity issue within 48 months. The average percentage is \Sexpr{round(mean(BB_with_ISS_later_total),1)}$\%$ and there are only \Sexpr{sum(BB_with_ISS_later_total > 10)} years (1989 and 1990) where the percentage is larger than $10\%$.

@@

The Calendar Method results in Panel B of Table~\ref{tbl:BBISSexit} show a relatively large drop of the excess returns over time (e.g., from \Sexpr{Exit_on_SEO_Abn_table_cal["+12",4]}$\%$ after 12 months to \Sexpr{Exit_on_SEO_Abn_table_cal["+48",4]}$\%$ after 48 months) indicating potential benefits of exiting a buyback position when there is a subsequent issue. Figure  \ref{fig:BBISSexit} (Panel~B) shows the benefits of exiting early. The figure shows a strategy with hindsight where, starting in \Sexpr{firstyear}, we invest in an equally weighted portfolio of only firms that announced a buyback and subsequently issued equity within the 48 months after the buyback announcement. The dashed line shows the cumulative excess return if we sold the stock whenever the firm issued shares within 48 months (the ``exit strategy''). The solid line shows the cumulative excess returns if we only sold 48 months after the buyback announcement (the ``no exit strategy''). The investor who had followed the exit strategy would have earned (after 30 years) a cumulative excess return of \Sexpr{round(tail(100*cumsum(BB_ISS_Exit_Hedged),1),1)}$\%$, compared to the \Sexpr{round(tail(100*cumsum(BB_ISS_NoExit_Hedged),1),1)}$\%$ of a buy and hold for 48 months strategy. Note, however, that because very few firms that buy back stock issue equity within 48 months,  a strategy ``without hindsight'' where one bought all companies after a buyback and sold only those after a subsequent equity issue would not substantially increase excess returns.

%Table~\ref{tbl:BBISSexitAfter} shows the long run excess returns after the announcement of an equity issue for two samples. The first sample (After a Buyback) shows the excess returns for issues for which in the previous 48 months the firm announced a buyback.  The second sample (No Prior Buyback) shows the excess returns for all other issue announcements.  The fact that excess returns are not significantly different from zero for the post-buyback issuers agrees with the intuition of Figure~\ref{fig:BBISSexit}: exiting when there is a subsequent equity issue is a better strategy for the long-term buyback investor.
